Catchability_ecov_sims

### 2023-09-26 Ecov_study/catchability/Catchability_ecov_sims.Rmd
Add model names and update sim test code.

@@

  # Finish setup & save OM
  OM <- NULL # Clear prior OM object just in case
  OM <- fit_wham(input = inputOM, do.fit = FALSE, MakeADFun.silent = TRUE)
  mkdir(here::here("Ecov_study", "catchability", "Results", paste0("OM_", OMsetup$OMname[iom]))) # set up storage
  saveRDS(OM, file = here::here("Ecov_study", "catchability", "Results", paste0("OM_", OMsetup$OMname[iom]), paste0("OM_", OMsetup$OMname[iom], ".Rds"))) # save OM
  saveRDS(OMsetup[iom,], file = here::here("Ecov_study", "catchability", "Results", paste0("OM_", OMsetup$OMname[iom]), "OMsettings.Rds")) # save OM settings in a separate file since naming is based on arbitraty order in OMsetup table

@@

@@

      # Catchability random effects
      inputEM <- set_q(input = inputEM, catchability = list(re = qRand))
    }

@@

### Test
```{r}
simTestWHAM(nsim = 5, OM = OM1, inputEMlist = list(EMq_env, EMq_rand_env, EMq_rand, EMq)) # Update once OM/EM specifics finalized!!!!

@@

# Run simulation tests
for(iom in 1:nrow(OMsetup)){
  omdir <- here::here("Ecov_study", "catchability", "Results", paste0("OM_", OMsetup[iom, "OMname"]))

@@

```
#### Alex run F_hist = Fmsy simulations
```{r}
# Set number of simulations to run
nsim <- 2

# Subset of OMs to run
OMsetup %>% filter(F_hist == "Fmsy")

@@

@@

### Run OMs with no ecov effect 
EMs with no ecov effect (NoEcov) and with ecov effect (Ecov) are equivalent when the OM has no ecov effect and the qRand and qRandEcov are also equivalent so only run the NoEcov and qRandEcov EMs for these OMs
```{r}
subsetOM <- OMsetup %>% filter(Ecov_effect == 0)
# EMs 
subsetEM <- EMsetup %>% filter(miss_season == "NONE") %>% filter(miss_q == "qRand" | miss_q == "NoEcov")
```

@@

```{r}
postprocess_simTestWHAM(filenames = c("filename1.Rds", "filename2.Rds", "ect.Rds")) # !!! Update once completed runs
```

@@

### Result formatted as list of lists, save as rdata object in specified directory with timestamp in name

run1_11_14_22.Rda\<-result - EM1 - EM2 - EM3 - EM4 - OM result

# Other things to consider

-   Other EMs can be developed (e.g. with alternative ecov process
    assumptions) but should be given DIFFERENT model_names to help with
    post-processing

# Short script for function testing purposes only!!!

```{r}
library(wham)
# For testing function
testdata <- read_asap3_dat(paste("/Users/amandahart/Research/Plaice_Methods_Development", "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit_fixSeason.DAT", sep="/")) # this can be swapped out for any ASAP file you have to set up a WHAM model for debugging
testinput <- prepare_wham_input(testdata)
testWHAM <- fit_wham(testinput, MakeADFun.silent = TRUE, do.osa = FALSE, do.retro=FALSE)

OM <- testWHAM
testinput1 <- prepare_wham_input(testdata, model_name = "test1")
testinput2 <- prepare_wham_input(testdata, model_name="test2")
testinput3 <- prepare_wham_input(testdata, model_name="test3")
inputEMlist <- list(testinput1, testinput2, testinput3)

test <- simTestWHAM(nsim = 2, OM = OM, inputEMlist = inputEMlist)
```

# To do next

- Finish OM setup
  - change how ecov passed in
  - set up range of uncertainty values to explore
  - tim sets equilibrium F (eq_F_init)
    - setup OM without fit & use model to find F40 proxy
  - Tim also sets intitial numbers at age based on equilibrium (overfished F=eqFN1*max_mult_Fmsy or not eqFN1=0)
- Tim lines 71-79 pf make_om use internal processing for prepare_wham_input to plug in setup from M_Ecov_om_setup.R
- Update what is saved as output
  - calculate performance metrics
- Run simulations, hpcc?
- Separate sims and function scripts

# 9/18/23
1) do OM & EM setup (EMs specified relative to each OM)
```{r}
Setup_OMs()
```
2) simulation test EMs for each OM
```{r}
simTestWHAM()
```
3) Post-process results
```{r}
postprocess_simTestWHAM()
```

>>>>

OMsetup[,"F_hist"] <- as.character(OMsetup[,"F_hist"])

@@

  # Finish setup & save OM
  inputOM$model_name <- paste0("OM_", paste(OMsetup[iom, ], collapse = "_")) # Set up OM name based on OMsetup 
  OM <- NULL # Clear prior OM object just in case
  OM <- fit_wham(input = inputOM, do.fit = FALSE, MakeADFun.silent = TRUE)
  mkdir(here::here("Ecov_study", "catchability", "Results", paste0("OM_", OMsetup$OMname[iom]))) # set up storage
  saveRDS(OM, file = here::here("Ecov_study", "catchability", "Results", paste0("OM_", OMsetup$OMname[iom]), paste0("OM_", OMsetup$OMname[iom], ".Rds"))) # save OM
  saveRDS(OMsetup[iom,], file = here::here("Ecov_study", "catchability", "Results", paste0("OM_", OMsetup$OMname[iom]), "OMsettings.Rds")) # save OM settings in a separate file since naming is based on arbitraty order in OMsetup table

@@

      # Set up EM name based on EMsetup
      input$model_name <- paste0("EM_", paste(unfactor(EMsetup[iem, ]), collapse = "_")) # Set up OM name based on OMsetup

@@

      # Set up EM name based on EMsetup
      input$model_name <- paste0("EM_", paste(unfactor(EMsetup[iem, ]), collapse = "_")) # Set up OM name based on OMsetup 
    }

@@

### Test
```{r}
#simTestWHAM(nsim = 5, OM = OM1, inputEMlist = list(EMq_env, EMq_rand_env, EMq_rand, EMq)) # Update once OM/EM specifics finalized!!!!

# Set number of simulations to run
nsim <- 2

# Subset of OMs to run
subsetOM <- OMsetup %>% filter(F_hist == "H-L") %>% head(n=2)

# Run simulation tests
for(iom in 1:nrow(subsetOM)){
  omdir <- here::here("Ecov_study", "catchability", "Results", paste0("OM_", OMsetup[iom, "OMname"]))

    # Run simulation test
    simTestWHAM(nsim = nsim,
                OM = testOM,
                inputEMlist = list(testEM), # Run one EM at a time
                outdir = here::here(omdir, paste0("EM_missSeason_", subsetEM[iem, "miss_season"], "_missQ_", subsetEM[iem, "miss_q"])))
  }
}
```

@@

# Run simulation tests
for(iom in 1:nrow(subsetOM)){
  omdir <- here::here("Ecov_study", "catchability", "Results", paste0("OM_", OMsetup[iom, "OMname"]))

@@

```
#### Alex run F_hist = Fmsy simulations
This code loops over the rows in subsetOM and subsetEM. The easiest way to run smaller chunks is to change the number of rows in subsetOM (i.e. run fewer OMs at once) or run fewer simulations. Results are all time-stamped and postprocess_simTestWHAM() is set up to combine multiple files so this won't cause processing issues later on.
```{r}
# Set number of simulations to run
nsim <- 100

# Subset of OMs to run
subsetOM <- OMsetup %>% filter(F_hist == "Fmsy") %>% filter(Ecov_effect != 0)

@@

# Run simulation tests
for(iom in 1:nrow(subsetOM)){
  omdir <- here::here("Ecov_study", "catchability", "Results", paste0("OM_", OMsetup[iom, "OMname"]))

@@

### Run OMs with no ecov effect 
EMs with no ecov effect (NoEcov) and with ecov effect (Ecov) are equivalent when the OM has no ecov effect and the qRand and qRandEcov are also equivalent so only run the NoEcov and qRandEcov EMs for these OMs
#### Amanda runs H-L Fhist
```{r}
# Set number of simulations to run
nsim <- 100

# Subset of OMs to run
subsetOM <- OMsetup %>% filter(F_hist == "H-L") %>% filter(Ecov_effect != 0)
# EMs 
subsetEM <- EMsetup %>% filter(miss_season == "NONE") %>% filter(miss_q == "qRand" | miss_q == "NoEcov")

# Run simulation tests
for(iom in 1:nrow(subsetOM)){
  omdir <- here::here("Ecov_study", "catchability", "Results", paste0("OM_", OMsetup[iom, "OMname"]))

    # Run simulation test
    simTestWHAM(nsim = nsim,
                OM = testOM,
                inputEMlist = list(testEM), # Run one EM at a time
                outdir = here::here(omdir, paste0("EM_missSeason_", subsetEM[iem, "miss_season"], "_missQ_", subsetEM[iem, "miss_q"])))
  }
}
```
#### Alex runs Fmsy Fhist
```{r}
# Set number of simulations to run
nsim <- 100

# Subset of OMs to run
subsetOM <- OMsetup %>% filter(F_hist == "Fmsy") %>% filter(Ecov_effect != 0)
# EMs 
subsetEM <- EMsetup %>% filter(miss_season == "NONE") %>% filter(miss_q == "qRand" | miss_q == "NoEcov")

# Run simulation tests
for(iom in 1:nrow(subsetOM)){
  omdir <- here::here("Ecov_study", "catchability", "Results", paste0("OM_", OMsetup[iom, "OMname"]))

    # Run simulation test
    simTestWHAM(nsim = nsim,
                OM = testOM,
                inputEMlist = list(testEM), # Run one EM at a time
                outdir = here::here(omdir, paste0("EM_missSeason_", subsetEM[iem, "miss_season"], "_missQ_", subsetEM[iem, "miss_q"])))
  }
}
```

@@

```{r}
# ID all simulation result files 
files <- list.files(path = here::here(), pattern = "simWHAM_", recursive = TRUE)

postprocess_simTestWHAM(filenames = files) 
```

@@

If results processed in batches/on multiple computers use combinePerfMet to combine final results
```{r}
